---
title: "KittyProduction"
output: html_document
---
Reading in the packages (the packages are already installed in the R environment)
```{r}
library(dplyr)
library(lubridate)
#library(Rcpp)                  #Dependency for dplyr
#library(rlang)                 #Dependency for dplyr
#library(pillar)                #Dependency for dplyr
library(ggplot2)
library(tidyverse)
#library(shiny)                 #Dependency for leaflet
library(leaflet)
library(RColorBrewer)
```
Set working directory
```{r}
setwd("/Users/charlesefox/Desktop/Work/Data From Mid-Con Energy")
```
Reading in the data
```{r}
setwd("/Users/charlesefox/Desktop/Work/Data From Mid-Con Energy")
Production <- read.csv(file = "Kitty.csv", header = TRUE, ",", stringsAsFactors = FALSE)
Header <- read.csv(file = "Header.csv", header = TRUE, ",", stringsAsFactors = FALSE)
Production$API  <- as.character(Production$API)
Header$API <- as.character(Header$API)
Production
Header
```
Grouping the data by API number
```{r}
ProdGroup <- group_by(Production, API)
ProdSum <- summarise(ProdGroup, 
                     oilcum = sum(OIL), 
                     gascum = sum(GAS), 
                     watercum = sum(WTR)
                     )
ProdSum
```



Join the files so that the production is tied to lat-longs
```{r}
JoinedFile <- merge(x=ProdSum, y=Header,by="API", all.x=FALSE, all.y=FALSE)
JoinedFile
```

Write the Joined file to a csv file 
```{r}
setwd("/Users/charlesefox/Desktop/Work/Data From Mid-Con Energy")
write.csv(JoinedFile, "JoinedFile.csv", row.names=TRUE)
```

Now join a new file so that the monthly data is tied to the Header File
This next few sections will create a plot of monthly producdtion for the field
```{r}
ProdJoinedFile <- merge(x=Production, y=Header,by="API", all.x=FALSE, all.y=FALSE)
ProdJoinedFile$DATE <- as.Date(ProdJoinedFile$DATE, format='%m/%d/%y')  
ProdJoinedFile
setwd("/Users/charlesefox/Desktop/Work/Data From Mid-Con Energy")
write.csv(ProdJoinedFile, "ProdJoinedFile.csv", row.names = TRUE)
```

Pull out one companies data
```{r}
ProdJoinedFile %>% filter(CurrentOperator == "MIDCON ENERGY OPERATING")
```


```{r}
p <- ggplot(ProdJoinedFile, aes(x=DATE, y=OIL)) +
  geom_area(color="black")
p
pg <- ggplot_build(p)
pg
setwd("/Users/charlesefox/Desktop/Work/Data From Mid-Con Energy")
write.csv(pg$data[[1]], "pg.csv", row.names = TRUE)
```
create an interactive map
```{r}
c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
   )
pie(rep(1, 25), col = c25)
popupinfo <- c(paste0("<b>", (JoinedFile$WellName),"<br/>",
                      "<b>", (JoinedFile$CurrentOperator), "<br>",
                      "<b> Cum Oil <b>", round(JoinedFile$oilcum), "<br/>",
                      "<b> Cum Gas <b>", round(JoinedFile$gascum),"<br/>",
                      "<b> Cum Wtr <b>", round(JoinedFile$watercum)))
pal <- colorNumeric(palette = "Set3", domain = JoinedFile$oilcum)
leaflet(data=JoinedFile) %>% 
  addTiles() %>%
  addCircleMarkers(data = JoinedFile, radius= ~oilcum/10000, lng = ~Longitude, lat = ~Latitude, popup = popupinfo,
#                   color = ~pal(oilcum)) %>%
                    color = "Blue") # %>%
#   addLegend(pal = pal, values = ~oilcum, opacity = 0.9, title = "Oil Cum, BO")
#  addLegend(pal = pal, values = ~oilcum, opacity = 0.9, title = "Oil Cum, BO")
          
```

this is a change